Finite-size scaling of free energy in the dimer model on a hexagonal domain

### 2019-08-03 AffineLieAlgebras/MQFT2018/paper.tex
Abstract fix

\begin{abstract}
  We consider dimer model on a hexagonal lattice. This model can be seen as a ``pile of cubes in the
  corner''. The energy of configuration is given by the volume of the pile and the partition
  function is computed by the classical MacMahon formula or, more formally, by the determinant of
  Kasteleyn matrix. We use the expression for the partition function to derive the scaling behavior
  of free energy in the limit of lattice mesh tending to zero and temperature tending to infinity.
  We discuss the universality and physical meaning of expansion coefficients.
\end{abstract}

@@

\begin{figure}[htbp]
\center{\scalebox{0.4}{\includegraphics{loz.eps}}}
\caption{\label{dhf}A configuration of dimers on the hexagonal lattice and a corresponding picture
  of ``cubes in the corner''.}
\end{figure}

>>>>

\begin{abstract}
  We consider dimer model on a hexagonal lattice. This model can be
  seen as a ``pile of cubes in the box''. The energy of configuration
  is given by the volume of the pile and the partition function is
  computed by the classical MacMahon formula or, more formally, by the
  determinant of Kasteleyn matrix. We use the expression for the
  partition function to derive the scaling behavior of free energy in
  the limit of lattice mesh tending to zero and temperature tending to
  infinity. We consider the cases of finite hexagonal domain, of
  infinite height box and coordinate-dependent Boltzmann weights. We
  obtain asymptotic expansion of free energy and discuss the
  universality and physical meaning of the expansion coefficients.
\end{abstract}

@@

\begin{figure}[htbp]
\center{\scalebox{0.4}{\includegraphics{loz}}}
\caption{\label{dhf}A configuration of dimers on the hexagonal lattice and a corresponding picture
  of ``cubes in the corner''.}
\end{figure}
